Gaia DR2 view of the GD-1 stellar stream

### 2018-04-26 paper/gd1.tex
ack eddie

% \usepackage{amsmath}

@@

\acknowledgements{
thanks: Belokurov, Casey, Geha, Hogg, Johnston, Koposov, Spergel
This research was started at the NYC Gaia DR2 Workshop at the Center for Computational Astrophysics of the Flatiron Institute in 2018 April.
AB acknowledges generous support from the Institute for Theory and Computation at Harvard University.
All code used in this work and all results are available at \url{https://github.com/adrn/GD1-DR2}.
}

>>>>

\usepackage{amsmath}

@@

\acknowledgements{
thanks: Belokurov, Casey, Geha, Hogg, Johnston, Koposov, Schlafly, Spergel
This research was started at the NYC Gaia DR2 Workshop at the Center for Computational Astrophysics of the Flatiron Institute in 2018 April.
AB acknowledges generous support from the Institute for Theory and Computation at Harvard University.
All code used in this work and all results are available at \url{https://github.com/adrn/GD1-DR2}.
}
